---
title: "sigurd version"
author: "Sigurd Fyhn Sørensen"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# START SPIVEY DATA 

## Packages
```{r}
pacman::p_load(readbulk)
pacman::p_load(MASS,lme4,GGally,ggpubr, reshape, boot)
pacman::p_load(ellipse, tidyverse, Hmisc)
pacman::p_load(pROC, devtools, reshape2, mousetrap)
pacman::p_load(lmerTest)
```


```{r}
spivey_df <- read_bulk("../Our_data/", extension = "csv")

```

## Load data 
```{r}
spivey_df_short <- spivey_df %>% 
  dplyr::select(left_stimuli_1, right_stimuli_1, timestamps_mouse, sound, practice, timestamps_mouse, xpos_mouse, ypos_mouse, response, response_time, count_trial_sequence, correct_response, correct, subject_nr, trial_type, live_row )

#write_csv(spivey_df_short, "mouse_spivey_short.csv")

spivey_df_short <- spivey_df_short %>% 
  filter(practice != "yes")
```


```{r}
t_test_accuracy <- spivey_df_short %>% 
  group_by(subject_nr, trial_type) %>% 
  dplyr::summarise(subject_accuracy = 1-sum(correct)/n())
```
```{r}
t_test_accuracy_wide <- pivot_wider(t_test_accuracy, names_from = trial_type, values_from = subject_accuracy)
t_test_accuracy %>% 
  group_by(trial_type) %>% 
  dplyr::summarise(mean = mean(subject_accuracy))
```


```{r}
t.test(t_test_accuracy_wide$cohort, t_test_accuracy_wide$control, paired = TRUE)

```
```{r}
#model_accuracy <- lmerTest::lmer(correct~trial_type + (1|subject_nr), data = spivey_df_short)
#summary(model_accuracy)
```

```{r}
spivey_df_filter <- spivey_df_short %>% 
  filter(correct == 1)
```

```{r}
t_test_response_time <- spivey_df_filter %>% 
  group_by(subject_nr, trial_type) %>% 
  dplyr::summarise(mean_response_time = mean(response_time))

t_test_response_time_wide <- pivot_wider(t_test_response_time, names_from = trial_type, values_from = mean_response_time)

t.test(t_test_response_time_wide$control, t_test_response_time_wide$cohort, paired = TRUE, alternative = "two.sided")
```
```{r}
mean(t_test_response_time_wide$cohort)
```

```{r}
mean(t_test_response_time_wide$control)
```


```{r}
model_response_time <- lmerTest::lmer(response_time~trial_type + (1|subject_nr), data = spivey_df_filter)
summary(model_response_time)
```





```{r}
#Subset for Accuracy == TRUE.
spivey_df_short_correct <- subset(spivey_df_short, correct == 1)
spivey_df_shot_correct <- subset(spivey_df_short_correct, practice == "no")

#TUrn Subject into factor
spivey_df_short_correct$subject_nr <- factor(spivey_df_short_correct$subject_nr)
```

# Mousetrap
```{r}
#creating mouse_trap object, extracting initiation times and creating a dataframe with only the relevant information
m <- mt_import_mousetrap(spivey_df_short_correct)

m_measures <- mt_measures(m)

data_initiation_time <- data.frame(subject_nr = spivey_df_short_correct$subject_nr, trial_type = spivey_df_short_correct$trial_type, initiation_time = m_measures$measures$initiation_time)
```

```{r}
head(data_initiation_time)
```


```{r}
t_test_initiation_time <- data_initiation_time %>% 
  group_by(subject_nr, trial_type) %>% 
  dplyr::summarise(mean_initiation_time = mean(initiation_time))

t_test_initiation_time_wide <- pivot_wider(t_test_initiation_time, names_from = trial_type, values_from = mean_initiation_time)

t.test(t_test_initiation_time_wide$control, t_test_initiation_time_wide$cohort, paired = TRUE, alternative = "two.sided")
```
```{r}
mean(t_test_initiation_time_wide$control)
```
```{r}
mean(t_test_initiation_time_wide$cohort)
```


```{r}
model_initiation_time <- lmerTest::lmer(initiation_time~trial_type + (1|subject_nr), data = data_initiation_time)
summary(model_initiation_time)
```

```{r}
data_duration_time <- data.frame(subject_nr = spivey_df_short_correct$subject_nr, trial_type = spivey_df_short_correct$trial_type, duration_time = spivey_df_short_correct$response_time - m_measures$measures$initiation_time, response_time = spivey_df_short_correct$response_time, initiation_time = m_measures$measures$initiation_time)
```

```{r}
head(data_duration_time)
```
```{r}
t_test_duration_time <- data_duration_time %>% 
  group_by(subject_nr, trial_type) %>% 
  dplyr::summarise(mean_duration_time = mean(duration_time))

t_test_duration_time_wide <- pivot_wider(t_test_duration_time, names_from = trial_type, values_from = mean_duration_time)

t.test(t_test_duration_time_wide$control, t_test_duration_time_wide$cohort, paired = TRUE, alternative = "two.sided")
```

```{r}
mean(t_test_duration_time_wide$control)
```
```{r}
mean(t_test_duration_time_wide$cohort)
```


```{r}
model_duration_time <- lmerTest::lmer(duration_time~trial_type + (1|subject_nr), data = data_duration_time)
summary(model_duration_time)
```


```{r}
m <- mt_import_mousetrap(spivey_df_short_correct)

#remap
m <- mt_remap_symmetric(m, use = 'trajectories', remap_xpos = "left", remap_ypos = "up")

m <- mt_exclude_initiation(m)
m <- mt_time_normalize(m_exclude_initiation, nsteps = 101) #creates tn_trajectories

#Final prep of data.
#Make the end and start point together. 
m <- mt_align(m, use = "tn_trajectories", save_as = "tn_align_trajec", dimensions = c("xpos", "ypos"), coordinates = "isotropic", align_start = TRUE , align_end = TRUE, align_side = "no", verbose = FALSE)

m <- mt_scale_trajectories(m, use = "tn_align_trajec", save_as = "final_trajec", c("xpos", "ypos"), center = TRUE, scale = TRUE, within_trajectory = FALSE, prefix = "z_", transform = NULL)

m <- mt_measures(m, use = 'tn_trajectories')
```

```{r}
'''Different methods have been suggested for assessing the bimodality of mouse-tracking measure
distributions, each of which has advantages and disadvantages (see Freeman & Dale, 2013).

Hehman et al. (2015) focus on two specific methods (bimodality coefficient and Hartigan’s dip
statistic) which are implemented here.

If methods include BC, the bimodality coefficient is calculated using the bimodality_coefficient
function in this package. According to Freeman and Ambady (2010), a distribution is considered
bimodal if BC > 0.555.

Note that MouseTracker (Freeman & Ambady, 2010) standardizes variables within each subject
before computing the BC. This is also possible here using mt_standardize (see Examples).

If methods include HDS, Hartigan’s dip statistic is calculated using the dip.test function of the
diptest package. The corresponding p value (computed via linear interpolation) is returned.

If methods include HDS_sim, Hartigan’s dip statistic is calculated using the dip.test function with
the additional argument simulate.p.values=TRUE. In this case, the p value is computed from a
Monte Carlo simulation of a uniform distribution with B (default: 2000) replicates.'''
```



```{r}
#for "degree of curvature" Spivey standardises based on only subject_nr
#I do not calculate "degree of curvature" but use "average deviation from direct path" instead

#mt_check_bimodality(m, use_variables=c("MAD", "AD"), methods = c("BC", "HDS"), grouping_variables="trial_type")
#mt_example <- mt_standardize(m, use_variables=c("MAD", "AD"), within="subject_nr")

m_standardised_subject_nr <- mt_standardize(m,use_variables=c("AD"), within=c("subject_nr"), prefix="z_")
mt_check_bimodality(m_standardised_subject_nr, use_variables=c("z_AD"), methods = c("BC"), grouping_variables="trial_type")
```


```{r}
#distributions of average deviation
data.frame(z_AD = m_standardised_subject_nr$measures$z_AD, trial_type = spivey_df_short_correct$trial_type) %>% 
  ggplot(aes(x = z_AD, fill = trial_type)) +
  geom_histogram(alpha = 0.5, position = "identity")
```
```{r}
df_zAD <- data.frame(z_AD = m_standardised_subject_nr$measures$z_AD, trial_type = spivey_df_short_correct$trial_type) 

df_zAD %>% 
  group_by(trial_type) %>%
  dplyr::summarise(mean(z_AD), variance = var(z_AD))
```

```{r}
#if Spivey actually just means AUC when talking about "degree of curvature" then the following could be used
m_standardised_subject_nr <- mt_standardize(m,use_variables=c("AUC"), within=c("subject_nr"), prefix="z_")
mt_check_bimodality(m_standardised_subject_nr, use_variables=c("z_AUC"), methods = c("BC"), grouping_variables="trial_type")
```

```{r}
df_zAUC <- data.frame(z_AUC = m_standardised_subject_nr$measures$z_AUC, trial_type = spivey_df_short_correct$trial_type) 

df_zAUC %>% 
  group_by(trial_type) %>%
  dplyr::summarise(mean = mean(z_AUC), variance = var(z_AUC))
```


```{r}
#for "area under trajectory" Spivey standardises based on subject_nr and trial_type

#mt_check_bimodality(m, use_variables=c("MAD", "AD"), methods = c("BC", "HDS"), grouping_variables="trial_type")
#mt_example <- mt_standardize(m, use_variables=c("MAD", "AD"), within="subject_nr")

m_standardised_subject_nr <- mt_standardize(m,use_variables=c("AUC"), within=c("subject_nr", "trial_type"), prefix="z_")

#if "degree of curvatur" actually just is "area under the curve" then the following would be the bimodality coefficient
mt_check_bimodality(m_standardised_subject_nr, use_variables=c("z_AUC"), methods = c("BC"), grouping_variables="trial_type")
```

```{r}
df_zAUC <- data.frame(z_AUC = m_standardised_subject_nr$measures$z_AUC, trial_type = spivey_df_short_correct$trial_type) 

df_zAUC %>% 
  group_by(trial_type) %>%
  dplyr::summarise(mean = mean(z_AUC), variance = var(z_AUC))

```
```{r}
df_zAUC%>% 
  ggplot(aes(x = z_AUC, fill = trial_type)) +
  geom_histogram(alpha = 0.5, position = "identity")
```


```{r}
ks.test(filter(df_zAUC, trial_type == "control")$z_AUC, filter(df_zAUC, trial_type == "cohort")$z_AUC)
```

```{r}

```




```{r}


#### FIX ### LOOK AT WITH NIELS.
#derivs calculated using tn (time normalized) (we did not space normalize but maybe that is ok)
m <- mt_derivatives(
  m,
  save_as = 'deriv',
  use = "tn_trajectories",
  dimensions = c("xpos", "ypos"),
  timestamps = "timestamps",
  prefix = "",
  absolute = FALSE,
  return_delta_time = FALSE,
  verbose = FALSE
)



derivs <- mt_export_wide(m$deriv)

toMatch <- c("acc", "vel", "time", "dist")
derivs <- derivs[, grepl(paste(toMatch, collapse = "|"), names(derivs))]

trajec <- mt_export_wide(m$final_trajec)
toMatch2 <- c("z_")
trajecs_ok <- trajec[, grepl(paste(toMatch2, collapse = "|"), names(trajec))]

spivey_df_data <- cbind(trajecs_ok, derivs, m$data)
```




### CREATE DATA FRAME WITH NORMALIZED POSITIONS, TIME, VELOCITY AND ACCELERATION. 
Same as normalized_positions for the negation data. 

```{r}
write_csv(spivey_df_data, "spivey_norm_derv_data.csv")
```

### Prepare data frame for PCA rename colnames to match. 
```{r}
#ORDER: X, Y, ACC, dist, time, vel
#DESIRED: X, y, V ,A 
oldnames <- c(colnames(spivey_df_data)[1:202],colnames(spivey_df_data)[506:606], colnames(spivey_df_data)[203:303])

#Time , X , Y , Steps, dist, vel , acc

new_names <- c(#paste0("t",sprintf('%0.3d', 1:101)),
  paste0("x",sprintf('%0.3d', 1:101)),
  paste0("y",sprintf('%0.3d', 1:101)),
  #paste0("s",sprintf('%0.3d', 1:101)),
  #paste0("d",sprintf('%0.3d', 1:101)),
  paste0("v",sprintf('%0.3d', 1:101)),
  paste0("a",sprintf('%0.3d', 1:101)))


pacman::p_load(data.table)


setnames(spivey_df_data, old = oldnames, new = new_names)

setnames(spivey_df_data, old = c("subject_nr", "live_row", "trial_type", "response"), new = c("Subject", "Item.number", "Polarity", "Response"))
```


```{r}
#Turn numeric
x <- paste0('x', sprintf("%03d", c(1:101)))
y <- paste0('y', sprintf("%03d", c(1:101)))
a <- paste0('a', sprintf("%03d", c(1:101)))
v <- paste0('v', sprintf("%03d", c(1:101)))
# <- paste0('t', sprintf("%03d", c(1:101)))


spivey_df_data[y] <- sapply(spivey_df_data[y],as.numeric)
spivey_df_data[x] <- sapply(spivey_df_data[x],as.numeric)
spivey_df_data[v] <- sapply(spivey_df_data[v],as.numeric)
spivey_df_data[a] <- sapply(spivey_df_data[a],as.numeric)
#normalized_positions_tr_spivey[t] <- sapply(normalized_positions_tr_spivey[t],as.numeric)

```


## Try and use the pca for prediction (same features as in the original data set for training)
```{r}
#Select only those with X,Y,V,A
all_data_columns_spivey <- names(dplyr::select(spivey_df_data,
                                          starts_with("x"),
                                          starts_with("y"),
                                          starts_with("v"),
                                          starts_with("a")))
  

normalized_positions.new.spivey <- spivey_df_data %>%
  dplyr::select(Subject, Item.number, Polarity, Response, one_of(all_data_columns_spivey))

#write_csv(normalized_positions.new.spivey, "spivey_data_normalized_newnames_subset.csv")
```

```{r}
#Find Constant Col's
constant_columns_ctl <- normalized_positions.new.spivey %>%
  filter(Polarity == "control") %>%
  dplyr::select(starts_with("x"), starts_with("y"), starts_with('v'), starts_with('a')) %>%
  find_constant

constant_columns_nctl <- normalized_positions.new.spivey %>%
  filter(Polarity == "cohort") %>%
  dplyr::select(starts_with("x"), starts_with("y"), starts_with('v'),starts_with('a')) %>%
  find_constant

constant_columns <- c(constant_columns_ctl, constant_columns_nctl)


#Remove constant col
normalized_positions_tr_spivey <- dplyr::select(normalized_positions.new.spivey,
                                           -one_of(constant_columns))

#Another way to remove constant col's
normalized_positions_tr_spivey_2 <- normalized_positions.new.spivey[ , which(apply(normalized_positions_tr_spivey, 2, var) != 0)]

```


```{r}
all_data_columns_spivey2 <- names(dplyr::select(normalized_positions_tr_spivey,
                                          starts_with("x"),
                                          starts_with("y"),
                                          starts_with("v"),
                                          starts_with("a")))

normalized_positions_tr_spivey[all_data_columns_spivey2] <- sapply(normalized_positions_tr_spivey[all_data_columns_spivey2],as.numeric)

final_PCA_DATA <- normalized_positions_tr_spivey %>% 
  dplyr::select(one_of(all_data_columns))

#Do PCA on the entire data
prcomp(final_PCA_DATA, center = TRUE, scale = TRUE)
```

## BEING ABLE TO USE PREDICT! 

```{r}
load("/Users/sigurd/Documents/Perception and Action/Perception-Action-Exam/R 2/LDA-Full.RData") #load m_pca etc. 

final_PCA_PREDICT <- normalized_positions.new.spivey %>% 
  dplyr::select(Subject, Item.number, Polarity, Response, one_of(all_data_columns)) %>% 
  mutate(Subject = as.factor(Subject)) %>% 
  mutate(Item.number = as.factor(Item.number)) %>% 
  mutate(Polarity = as.factor(Polarity)) %>% 
  mutate(Response = as.factor(Response))

#Flip X
X_data_columns_spivey <- names(dplyr::select(final_PCA_PREDICT,
                                          starts_with("x")))
#Flip X
final_PCA_PREDICT[X_data_columns_spivey] <- final_PCA_PREDICT[X_data_columns_spivey]*-1

#Numeric
final_PCA_PREDICT[all_data_columns] <- sapply(final_PCA_PREDICT[all_data_columns],as.numeric)

#TIME TO PREDICT
predict(m_pca, final_PCA_PREDICT)


# Test names
colnames(final_PCA_PREDICT) == colnames(normalized_positions.new)
ncol(final_PCA_PREDICT) == ncol(normalized_positions.new)

as.data.frame(final_PCA_PREDICT)
as.data.frame(normalized_positions.new)
```


```{r}
#Do PCA
normalized_positions.new_pca_spivey <- bind_cols(normalized_positions.new,
                                          as.data.frame(predict(m_pca, normalized_positions_tr_spivey)[,1:n_pca]))
```




## TENDENCY IN TWO CONDITIONS. 
```{r}

mt_measures_aggre <-  mt_aggregate(
  m,
  use = 'measures',
  #use_variables = c('MAD', 'xpos_flips','AUC', 'RT'), # if you want all of the measures, exclude this line 
  use2_variables = 'trial_type')

mt_measures_aggre

```