---
title: "sigurd version"
author: "Sigurd Fyhn Sørensen"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# START SPIVEY DATA 

## Packages
```{r}
pacman::p_load(tidyverse, lme4, readbulk)
pacman::p_load(MASS,lme4,GGally,ggpubr, reshape, boot)
pacman::p_load(ellipse, tidyverse, Hmisc, plyr)
pacman::p_load(pROC, devtools, reshape2, mousetrap)
```

## Functions
```{r}
find_constant <- function(d, epsilon=1e-4) {
  names(d)[apply(d,2,function(x) is.na(var(x)) || sqrt(var(x)) < epsilon)]
}
```


## Load in Data
```{r}
spivey_df <- read_bulk("../Our_data")
```

```{r}
#Subset for the relevant columns.  
spivey_df_short <- spivey_df %>% 
  dplyr::select(left_stimuli_1, right_stimuli_1, timestamps_mouse, sound, practice, timestamps_mouse, xpos_mouse, ypos_mouse, response, response_time, count_trial_sequence, correct_response, correct, subject_nr, trial_type, live_row )

write_csv(spivey_df_short, "mouse_spivey_short.csv")

```

```{r}
#Subset for Accuracy == TRUE.
spivey_df_short_correct <- subset(spivey_df_short, correct == 1)
spivey_df_short_correct <- subset(spivey_df_short_correct, practice == "no")

#TUrn Subject into factor
spivey_df_short_correct$subject_nr <- factor(spivey_df_short_correct$subject_nr)
```


```{r}
#Percentage correct.
print(c(nrow(spivey_df_short_correct)/nrow(spivey_df_short)*100, "% correct"))
```

# Mousetrap
```{r}
m <- mt_import_mousetrap(spivey_df_short_correct)
```

```{r}
#First look at data. 
mt_plot(data = m , use = "trajectories", color = "trial_type")
```

```{r}
#remap (flip X-coordinates so target is always on the same side)
m <- mt_remap_symmetric(
  m, 
  use = 'trajectories',
  remap_xpos = "left"
  )

mt_plot(
  m, 
  use = 'trajectories',
  color = 'trial_type'
  )
```
```{r}
# plot with timestamps
mt_plot(
  m, 
  x = 'timestamps', # modifying the x-axis to plot timestamps
  y = 'xpos',       # modifying the y-axis to plot the xpos
  use = 'trajectories',
  color = 'trial_type' 
)
```
```{r}
#Remove initiation. 

m <- mt_exclude_initiation(m)
mt_plot(
  m, 
  x = 'timestamps',
  y = 'xpos',
  use = 'trajectories',
  color = 'trial_type' 
)
```
```{r}
# Time normalize
m <- mt_time_normalize(m, nsteps = 101) #creates tn_trajectories

mt_plot(
  m, 
  use = 'tn_trajectories',
  color = 'trial_type'
)

```


```{r}
#Make the end and start point together. 
m <- mt_align(
  m,
  use = "tn_trajectories",
  save_as = "tn_align_trajec",
  dimensions = c("xpos", "ypos"),
  coordinates = "norm",
  align_start = TRUE ,
  align_end = TRUE,
  align_side = "no",
  verbose = FALSE
)


#Standardize trajectories following Z-distirbution 
m <- mt_scale_trajectories(
  m,
  use = "tn_align_trajec",
  save_as = "final_trajec",
  c("xpos", "ypos"),
  center = TRUE,
  scale = TRUE,
  within_trajectory = FALSE,
  prefix = "z_",
  transform = NULL
)


```

```{r}
#Show average trajectories for the two curves 
mt_plot_aggregate(
  m, 
  use = 'tn_align_trajec',
  color = 'trial_type'
) + 
  labs(
    title = 'Aggregated time-normalized mouse trajectories')
```


# Getting Final Mouse Tracking measures such as acceleration, velocity, AUC etc. 
```{r}
#Measures calculated using tn (time normalized and space normalized)
m <- mt_measures(
  m,
  use = 'tn_trajectories')


#### FIX ### LOOK AT WITH NIELS.
#derivs calculated using tn (time normalized) (we did not space normalize but maybe that is ok)
m <- mt_derivatives(
  m,
  save_as = 'deriv',
  use = "tn_trajectories",
  dimensions = c("xpos", "ypos"),
  timestamps = "timestamps",
  prefix = "",
  absolute = FALSE,
  return_delta_time = FALSE,
  verbose = FALSE
)
```


```{r}
derivs <- mt_export_wide(m$deriv)

toMatch <- c("acc", "vel", "time", "dist")
derivs <- derivs[, grepl(paste(toMatch, collapse = "|"), names(derivs))]

trajec <- mt_export_wide(m$final_trajec)
toMatch2 <- c("z_")
trajecs_ok <- trajec[, grepl(paste(toMatch2, collapse = "|"), names(trajec))]

#Combine trajectories, derivatives and other mouse data into 1 data frame. 
spivey_df_data <- cbind(trajecs_ok, derivs, m$data)
```



### CREATE DATA FRAME WITH NORMALIZED POSITIONS, TIME, VELOCITY AND ACCELERATION. 
Same as normalized_positions for the negation data. 

```{r}
write_csv(spivey_df_data, "spivey_norm_derv_data.csv")
```

### Prepare data frame for PCA rename colnames to match. 
```{r}
#ORDER: X, Y, ACC, dist, time, vel
#DESIRED: X, y, V ,A 
oldnames <- c(colnames(spivey_df_data)[1:202],colnames(spivey_df_data)[506:606], colnames(spivey_df_data)[203:303])

#Time , X , Y , Steps, dist, vel , acc

new_names <- c(#paste0("t",sprintf('%0.3d', 1:101)),
  paste0("x",sprintf('%0.3d', 1:101)),
  paste0("y",sprintf('%0.3d', 1:101)),
  #paste0("s",sprintf('%0.3d', 1:101)),
  #paste0("d",sprintf('%0.3d', 1:101)),
  paste0("v",sprintf('%0.3d', 1:101)),
  paste0("a",sprintf('%0.3d', 1:101)))


pacman::p_load(data.table)


setnames(spivey_df_data, old = oldnames, new = new_names)

setnames(spivey_df_data, old = c("subject_nr", "live_row", "trial_type", "response"), new = c("Subject", "Item.number", "Polarity", "Response"))
```


```{r}
#Turn numeric
x <- paste0('x', sprintf("%03d", c(1:101)))
y <- paste0('y', sprintf("%03d", c(1:101)))
a <- paste0('a', sprintf("%03d", c(1:101)))
v <- paste0('v', sprintf("%03d", c(1:101)))
# <- paste0('t', sprintf("%03d", c(1:101)))


spivey_df_data[y] <- sapply(spivey_df_data[y],as.numeric)
spivey_df_data[x] <- sapply(spivey_df_data[x],as.numeric)
spivey_df_data[v] <- sapply(spivey_df_data[v],as.numeric)
spivey_df_data[a] <- sapply(spivey_df_data[a],as.numeric)
#normalized_positions_tr_spivey[t] <- sapply(normalized_positions_tr_spivey[t],as.numeric)

```


## Try and use the pca for prediction (same features as in the original data set for training)
```{r}
#Select only those with X,Y,V,A
all_data_columns_spivey <- names(dplyr::select(spivey_df_data,
                                          starts_with("x"),
                                          starts_with("y"),
                                          starts_with("v"),
                                          starts_with("a")))
  

normalized_positions.new.spivey <- spivey_df_data %>%
  dplyr::select(Subject, Item.number, Polarity, Response, one_of(all_data_columns_spivey))

#write_csv(normalized_positions.new.spivey, "spivey_data_normalized_newnames_subset.csv")
```

```{r}
#Find Constant Cols
constant_columns_ctl <- normalized_positions.new.spivey %>%
  filter(Polarity == "control") %>%
  dplyr::select(starts_with("x"), starts_with("y"), starts_with('v'), starts_with('a')) %>%
  find_constant

constant_columns_nctl <- normalized_positions.new.spivey %>%
  filter(Polarity == "cohort") %>%
  dplyr::select(starts_with("x"), starts_with("y"), starts_with('v'),starts_with('a')) %>%
  find_constant

constant_columns <- c(constant_columns_ctl, constant_columns_nctl)


#Remove constant col
normalized_positions_tr_spivey <- dplyr::select(normalized_positions.new.spivey,
                                           -one_of(constant_columns))




#Another way to remove constant col's
normalized_positions_tr_spivey_2 <- normalized_positions.new.spivey[ , which(apply(normalized_positions_tr_spivey, 2, var) != 0)]

```


```{r}
all_data_columns_spivey2 <- names(dplyr::select(normalized_positions_tr_spivey,
                                          starts_with("x"),
                                          starts_with("y"),
                                          starts_with("v"),
                                          starts_with("a")))

normalized_positions_tr_spivey[all_data_columns_spivey2] <- sapply(normalized_positions_tr_spivey[all_data_columns_spivey2],as.numeric)
```


```{r}
#normalized_positions.new_pca_spivey <- bind_cols(normalized_positions_tr_spivey,
#                                          as.data.frame(predict(our_model, final_PCA_DATA)[,1:13]))

#lda_measure.new.df_spivey <- data_frame(
 # lda_measure=c(as.matrix(dplyr::select(normalized_positions.new_pca_spivey, starts_with("PC"))) %*% v_lda- b_lda),
  #Subject = normalized_positions.new_pca_spivey$Subject, 
#  Item.number = normalized_positions.new_pca_spivey$Item.number, 
 # Polarity = normalized_positions.new_pca_spivey$Polarity, 
  #Response = normalized_positions.new_pca_spivey$Response)


# ggplot(lda_measure.new.df_spivey, aes(x = lda_measure, col = Polarity)) + geom_density()
```

## BEING ABLE TO USE PREDICT not possible...! 

```{r}
#Experiment but didn't work. 
load("/Users/sigurd/Documents/Perception and Action/Perception-Action-Exam/R 2/LDA-Full.RData") #load m_pca etc. 

final_PCA_PREDICT <- normalized_positions.new.spivey %>% 
  dplyr::select(Subject, Item.number, Polarity, Response, one_of(all_data_columns)) %>% 
  mutate(Subject = as.factor(Subject)) %>% 
  mutate(Item.number = as.factor(Item.number)) %>% 
  mutate(Polarity = as.factor(Polarity)) %>% 
  mutate(Response = as.factor(Response))





#Flip X
X_data_columns_spivey <- names(dplyr::select(final_PCA_PREDICT,
                                          starts_with("x")))
#Flip X
final_PCA_PREDICT[X_data_columns_spivey] <- final_PCA_PREDICT[X_data_columns_spivey]*-1

#Numeric
final_PCA_PREDICT[all_data_columns] <- sapply(final_PCA_PREDICT[all_data_columns],as.numeric)
```


```{r}
#CSV FILE FOR 
csv_file_for_python = cbind(final_PCA_PREDICT, m$measures)
#write 
write_csv(final_PCA_PREDICT, "spivey_data_for_pca.csv")
```


```{r}
#FILE USED in Python script. 
write_csv(csv_file_for_python, "spivey_data_for_python.csv")
```


```{r}
#TIME TO PREDICT
#predict(m_pca, final_PCA_PREDICT)


# Test names to see if they match. 
#colnames(final_PCA_PREDICT) == colnames(normalized_positions.new)
#ncol(final_PCA_PREDICT) == ncol(normalized_positions.new)


```


```{r}
#Do PCA
normalized_positions.new_pca_spivey <- bind_cols(normalized_positions.new,
                                          as.data.frame(predict(m_pca, normalized_positions_tr_spivey)[,1:n_pca]))
```




## TENDENCY IN TWO CONDITIONS. 
```{r}

mt_measures_aggre <-  mt_aggregate(
  m,
  use = 'measures',
  #use_variables = c('MAD', 'xpos_flips','AUC', 'RT'), # if you want all of the measures, exclude this line 
  use2_variables = 'trial_type')

mt_measures_aggre

```